\documentclass[11pt,fleqn]{article}

\setlength {\topmargin} {-.15in}
\setlength {\textheight} {8.6in}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{automata,positioning,arrows}
\usepackage{diagbox}
\usepackage{stackrel}
\usepackage{fullpage}

\renewcommand{\labelenumi}{\theenumi.}
\renewcommand{\labelenumii}{\theenumii.}
\renewcommand{\labelenumiii}{\theenumiii.}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}}
\newcommand{\bsp}{\begin{sloppypar}}
\newcommand{\esp}{\end{sloppypar}}
\newcommand{\mname}[1]{\mbox{\sf #1}}
\newcommand{\sB}{\mbox{$\cal B$}}
\newcommand{\sC}{\mbox{$\cal C$}}
\newcommand{\sF}{\mbox{$\cal F$}}
\newcommand{\sM}{\mbox{$\cal M$}}
\newcommand{\sP}{\mbox{$\cal P$}}
\newcommand{\sV}{\mbox{$\cal V$}}
\newcommand{\set}[1]{{\{ #1 \}}}
\newcommand{\Neg}{\neg} 
\ifdefined \And 
\renewcommand{\And}{\wedge}
\else
\newcommand{\And}{\wedge}
\fi
\newcommand{\Or}{\vee}
\newcommand{\Implies}{\Rightarrow}
\newcommand{\Iff}{\Leftrightarrow}
\newcommand{\Forall}{\forall}
\newcommand{\ForallApp}{\forall\,}
\newcommand{\Forsome}{\exists}
\newcommand{\ForsomeApp}{\exists\,}
\newcommand{\mdot}{\mathrel.}
\newcommand{\der}[2]{\stackrel[#2]{#1}{\longrightarrow}}

\begin{document}

\begin{center}

  {\large \textbf{COMPSCI/SFWRENG 2FA3}}\\[2mm]
  {\large \textbf{Discrete Mathematics with Applications II}}\\[2mm]
  {\large \textbf{Winter 2020}}\\[8mm]
  {\huge \textbf{Assignment 9}}\\[6mm]
  {\large \textbf{Dr.~William M. Farmer}}\\[2mm]
  {\large \textbf{McMaster University}}\\[6mm]
  {\large Revised: March 21, 2020}

\end{center}

\medskip

Assignment 9 consists of two problems.  You must write your solutions
to the problems using LaTeX.

Please submit Assignment~9 as two files,
\texttt{Assignment\_9\_\emph{YourMacID}.tex} and
\texttt{Assignment\_9\_\emph{YourMacID}.pdf}, to the Assignment~9
folder on Avenue under Assessments/Assignments.
\texttt{\emph{YourMacID}} must be your personal MacID (written without
capitalization).  The \texttt{Assignment\_9\_\emph{YourMacID}.tex}
file is a copy of the LaTeX source file for this assignment
(\texttt{Assignment\_9.tex} found on Avenue under
Contents/Assignments) with your solution entered after each problem.
The \texttt{Assignment\_9\_\emph{YourMacID}.pdf} is the PDF output
produced by executing

\begin{itemize}

  \item[] \texttt{pdflatex Assignment\_9\_\emph{YourMacID}}

\end{itemize}

This assignment is due \textbf{Sunday, March 29, 2020 before
  midnight.}  You are allow to submit the assignment multiple times,
but only the last submission will be marked.  \textbf{Late submissions
  and files that are not named exactly as specified above will not be
  accepted!}  It is suggested that you submit your preliminary
\texttt{Assignment\_9\_\emph{YourMacID}.tex} and
\texttt{Assignment\_9\_\emph{YourMacID}.pdf} files well before the
deadline so that your mark is not zero if, e.g., your computer fails
at 11:50 PM on March 29.

\textbf{Although you are allowed to receive help from the
  instructional staff and other students, your submission must be your
  own work.  Copying will be treated as academic dishonesty! If any of
  the ideas used in your submission were obtained from other students
  or sources outside of the lectures and tutorials, you must
  acknowledge where or from whom these ideas were obtained.}

\newpage

\subsection*{Problems}

\be

  \item \textbf{[10 points]} Construct a regular grammar that
    generates the language matched by the regular expression $(000^* +
    111^*)^*$.

  \bigskip

  \textcolor{blue}{\textbf{Name: Hishmat Salehi \\
MacID: Salehh6 \\
Date: \today}}

Let $G = (\set{S,A,B},\set{0,1}, P, S)$ be the regular grammar where $P$ contains the following productions: \\
$S \rightarrow \epsilon \mid 00A \mid 11B$ \\
$A \rightarrow 0A \mid \epsilon \mid E$ \\
$B \rightarrow 1B \mid \epsilon \mid E$

  \item \textbf{[10 points]} Let $\Sigma = \set{a,b}$ and $L = \set{x
    \in \Sigma^* \mid x \not= \mname{rev}(x)}$.  Construct a simple
    grammar for $L$ as well as grammars in Chomsky and Greibach normal
    form for $L$.

  \bigskip

  \textcolor{blue}{\textbf{Name: Hishmat Salehi \\
MacID: Salehh6 \\
Date: \today}}

  \textcolor{red}{\textbf{Simple Grammar:}} \\
Let $G = (\set{S,A,B},\set{a,b}, P, S)$ be a simple grammar where $P$ contains the following productions: \\
$S \rightarrow aBb \mid bBa \mid aBbA \mid bBaA \mid AaBb \mid AbBa \mid AaBbA \mid AbBaA$ \\
$A \rightarrow Aa \mid a \mid Ab \mid b$ \\
$B \rightarrow aBa \mid bBb \mid \epsilon$ 

  \textcolor{red}{\textbf{Chomsky Normal Form:}} \\
Let $G = (\set{S,A,B,C,D},\set{a,b}, P, S)$ be a grammar in CNF form where $P$ contains the following productions: \\
$S \rightarrow ADB \mid BDA \mid ADBC \mid BDAC \mid CADB \mid CBDA \mid CADBC \mid CBDAC$ \\
$C \rightarrow CA \mid A \mid CB \mid B$ \\
$D \rightarrow ADA \mid BDB \mid AA \mid BB$ \\
$A \rightarrow a$ \\
$B \rightarrow b$ 

  \textcolor{red}{\textbf{Greibach Normal Form:}} \\
Let $G = (\set{S,A,B,C,D,N},\set{a,b}, P, S)$ be a grammar in GNF form where $P$ contains the following productions: \\
$S \rightarrow aDB \mid bDA \mid aDBC \mid bDAC \mid aN \mid bN$ \\
$C \rightarrow aC \mid a \mid bC \mid b$ \\
$N \rightarrow aCADB \mid bCADB \mid aCBDA \mid bCBDA \mid aCADBC \mid bCADBC \mid aCBDAC \mid bCBDAC$ \\
$D \rightarrow aDA \mid bDB \mid aA \mid bB$ \\
$A \rightarrow a$ \\
$B \rightarrow b$ \\

\ee

\end{document}


